% the acknowledgments section

I would like to thank my advisor, Prof. Jene Golovchenko, for all of his support and guidance through the years.  He taught me about rigorous science and the value of creativity and questioning assumptions.  He allowed me to pursue my own creativity throughout my time in his lab.  I would also like to thank Prof. Daniel Branton for his continual inspiration, feedback, and encouragement, as well as Prof. Lene Hau for her advice and enthusiasm for scientific discovery.

My fellow members of the Golovchenko group were constant sources of support, encouragement, and friendship, and my graduate school experience would not have been the same without them.  I wish to thank Drs. Bo Lu, Tamas Szalay, Aaron Kuan, Ryan Rollings, Edlyn Levine, and Don Dressen, as well as Gaku Nagashima, Eric Brandin, and Peter Frisella, for making my time in the group so enjoyable.  Special thanks go to Dr. Bo Lu, who has been my friend and collaborator on much of the work presented here.  Special thanks as well go to Eric Brandin, who helped me with experiments every day in the lab.

Most of all, I would like to thank my family.  My parents, Mary Kay and Don, always fostered in me a spirit of creativity and curiosity, and encouraged me in everything I did.  They made me believe that there were truly no limits on what I could achieve, and they made everything possible for me.  My sister, Julie, has always been there for me and supported me, and she and I went through graduate school together.  My lifelong friend Bryce Read, basically family, has never wavered in his friendship and his belief in me, and that means more than anything.  And finally I would like to thank my wonderful wife, Dr. Kayla Wheeler, who has been here with me on this long graduate school journey.  Her constant support and encouragement have been invaluable, and I could not have done it without her.